\textbf{Supplementary Material}

### 2021-07-09 submission/supplementary.tex

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  12pt,
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Supplementary Information},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1.0in]{geometry}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{times} % Times New Roman font
\usepackage[T1]{fontenc}

@@

\usepackage[labelsep=period, labelfont=bf]{caption}
\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\figurename}{Fig.}
\renewcommand{\thetable}{S\arabic{table}}
\captionsetup{justification=raggedright,singlelinecheck=false}

@@

\renewcommand{\figureautorefname}{Fig.}

\usepackage{microtype}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

\title{\textbf{Supplementary Information}}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{\textbf{Seasonal Dynamics of Epiphytic Microbial Communities on Marine
Macrophyte Surfaces}}
\author{}
\date{\vspace{-2.5em}}

@@

\vspace{20mm}

@@

{\centering \includegraphics[width=0.85\linewidth]{/mydisk/POSAO2/isabella/Korlevic_EpiphyticDynamics_FrontMicrobiol_2021/results/figures/rarefaction}

@@

{\centering \includegraphics[width=0.85\linewidth]{/mydisk/POSAO2/isabella/Korlevic_EpiphyticDynamics_FrontMicrobiol_2021/results/figures/calculators}

@@

{\centering \includegraphics[width=0.85\linewidth]{/mydisk/POSAO2/isabella/Korlevic_EpiphyticDynamics_FrontMicrobiol_2021/results/figures/chloroplast_bar_plot}

@@

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  12pt,
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Supplementary Material},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1.0in]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{times} % Times New Roman font
\usepackage[T1]{fontenc}

@@

\usepackage[labelsep=period, labelfont=bf]{caption}
\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\figurename}{Figure}
\renewcommand{\thetable}{S\arabic{table}}
\captionsetup{justification=raggedright,singlelinecheck=false}

@@

\renewcommand{\figureautorefname}{Figure}

\usepackage{microtype}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\title{\textbf{Supplementary Material}}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{\textbf{Seasonal Dynamics of Epiphytic Microbial Communities
on Marine Macrophyte Surfaces}}
\author{}
\date{\vspace{-2.5em}}

@@

\vspace{10mm}

@@

{\centering \includegraphics[width=0.85\linewidth]{/home/marino/Desktop/repositories/Korlevic_EpiphyticDynamics_FrontMicrobiol_2021/results/figures/rarefaction}

@@

{\centering \includegraphics[width=0.85\linewidth]{/home/marino/Desktop/repositories/Korlevic_EpiphyticDynamics_FrontMicrobiol_2021/results/figures/calculators}

@@

{\centering \includegraphics[width=0.85\linewidth]{/home/marino/Desktop/repositories/Korlevic_EpiphyticDynamics_FrontMicrobiol_2021/results/figures/chloroplast_bar_plot}

@@

\begin{longtable}[t]{>{\centering\arraybackslash}m{10em}>{\centering\arraybackslash}m{10em}cc>{\centering\arraybackslash}m{6em}>{\centering\arraybackslash}m{6em}}
\caption{\label{tab:calculators}Richness estimators and diversity indices of each community type. Calculations were done after normalization to the minimum number of reads per sample.\label{calculators_community_type}}\\
\toprule
\textbf{Community Type} & \textbf{Observed No. of OTUs} & \textbf{Chao1} & \textbf{ACE} & \textbf{Exponential Shannon} & \textbf{Inverse Simpson}\\
\midrule
\endfirsthead
\caption[]{Richness estimators and diversity indices of each community type. Calculations were done after normalization to the minimum number of reads per sample.\label{calculators_community_type} \textit{(continued)}}\\
\toprule
\textbf{Community Type} & \textbf{Observed No. of OTUs} & \textbf{Chao1} & \textbf{ACE} & \textbf{Exponential Shannon} & \textbf{Inverse Simpson}\\
\midrule
\endhead

\endfoot
\bottomrule
\endlastfoot
Seawater & 531.0  ±  143.9 & 1,244.5  ±  392.7 & 1,441.1  ±  458.7 & 62.2  ±   20.5 & 26.7  ±   8.0\\
\textit{Cymodocea nodosa} (Mixed) & 1,063.7  ±  210.6 & 1,703.2  ±  409.9 & 1,838.8  ±  437.3 & 237.8  ±  100.4 & 76.9  ±  46.6\\
\textit{Caulerpa cylindracea} (Mixed) & 1,688.4  ±  136.6 & 2,936.9  ±  460.2 & 3,220.7  ±  497.2 & 410.4  ±   92.5 & 102.2  ±  47.2\\
\textit{Caulerpa cylindracea} (Monospecific) & 1,750.4  ±  165.7 & 2,911.0  ±  575.0 & 3,171.7  ±  622.1 & 496.4  ±   87.1 & 144.4  ±  42.6\\*
\end{longtable}
\endgroup{}

\newpage

\input{../results/numerical/calculator_statistics.tex}

\newpage
\blandscape
\begingroup\fontsize{9}{11}\selectfont

\begin{longtable}[t]{>{\centering\arraybackslash}m{8em}ccl}
\caption{\label{tab:core_otus_taxonomy_table}Taxonomic classification of OTUs present at every sampling date in the each community type. Only ten OTUs with the highest number of sequences after normalization to the minimum number of reads per sample are shown. NR -- No Relative (sequences without known relatives within the corresponding group)\label{core_otus_taxonomy_table}}\\
\toprule
\textbf{Community Type} & \textbf{OTU Number} & \textbf{No. of Sequences} & \textbf{OTU Taxonomy}\\
\midrule
\endfirsthead
\caption[]{Taxonomic classification of OTUs present at every sampling date in the each community type. Only ten OTUs with the highest number of sequences after normalization to the minimum number of reads per sample are shown. NR -- No Relative (sequences without known relatives within the corresponding group)\label{core_otus_taxonomy_table} \textit{(continued)}}\\
\toprule
\textbf{Community Type} & \textbf{OTU Number} & \textbf{No. of Sequences} & \textbf{OTU Taxonomy}\\
\midrule
\endhead
 & Otu00014 & 5092 & \textit{Bacteria}; \textit{Proteobacteria}; \textit{Alphaproteobacteria}; \textit{Rhodobacterales}; \textit{Rhodobacteraceae}; \textit{Rhodobacteraceae} (NR)\\
\nopagebreak
 & Otu00020 & 3188 & \textit{Bacteria}; \textit{Proteobacteria}; \textit{Alphaproteobacteria}; \textit{Rhodobacterales}; \textit{Rhodobacteraceae}; \textit{Rhodobacteraceae} (NR)\\
\nopagebreak
 & Otu00019 & 3026 & \textit{Bacteria}; \textit{Cyanobacteria}; \textit{Cyanobacteriia}; \textit{Cyanobacteriales}; \textit{Xenococcaceae}; \textit{Pleurocapsa}\\
\nopagebreak
 & Otu00030 & 2014 & \textit{Bacteria}; \textit{Proteobacteria}; \textit{Alphaproteobacteria}; \textit{Rhodobacterales}; \textit{Rhodobacteraceae}; \textit{Rhodobacteraceae} (NR)\\
\nopagebreak
 & Otu00013 & 1884 & \textit{Bacteria}; \textit{Proteobacteria}; \textit{Alphaproteobacteria}; \textit{Rhodobacterales}; \textit{Rhodobacteraceae}; \textit{Rhodobacteraceae} (NR)\\
\nopagebreak
 & Otu00032 & 1586 & \textit{Bacteria}; \textit{Verrucomicrobiota}; \textit{Verrucomicrobiae}; \textit{Opitutales}; \textit{Puniceicoccaceae}; \textit{Lentimonas}\\
\nopagebreak
 & Otu00059 & 1469 & \textit{Bacteria}; \textit{Proteobacteria}; \textit{Gammaproteobacteria}; \textit{Burkholderiales}; \textit{Methylophilaceae}; \textit{Methylotenera}\\
\nopagebreak
 & Otu00005 & 1337 & \textit{Bacteria}; \textit{Proteobacteria}; \textit{Alphaproteobacteria}; \textit{Rhodobacterales}; \textit{Rhodobacteraceae}; \textit{Rhodobacteraceae} (NR)\\
\nopagebreak
 & Otu00050 & 1264 & \textit{Bacteria}; \textit{Proteobacteria}; \textit{Alphaproteobacteria}; \textit{Rhodobacterales}; \textit{Rhodobacteraceae}; \textit{Rhodobacteraceae} (NR)\\
\nopagebreak
\multirow{-10}{8em}{\centering\arraybackslash \textit{Cymodocea nodosa} (Mixed)} & Otu00029 & 1162 & \textit{Bacteria}; \textit{Proteobacteria}; \textit{Alphaproteobacteria}; \textit{Rhodobacterales}; \textit{Rhodobacteraceae}; \textit{Rhodobacteraceae} (NR)\\
\cmidrule{1-4}\pagebreak[0]
 & Otu00011 & 4051 & \textit{Bacteria}; \textit{Desulfobacterota}; \textit{Desulfobacteria}; \textit{Desulfobacterales}; \textit{Desulfosarcinaceae}; \textit{Desulfatitalea}\\
\nopagebreak
 & Otu00010 & 3436 & \textit{Bacteria}; \textit{Desulfobacterota}; \textit{Desulfobulbia}; \textit{Desulfobulbales}; \textit{Desulfocapsaceae}; \textit{Desulfocapsaceae} (NR)\\
\nopagebreak
 & Otu00013 & 2531 & \textit{Bacteria}; \textit{Proteobacteria}; \textit{Alphaproteobacteria}; \textit{Rhodobacterales}; \textit{Rhodobacteraceae}; \textit{Rhodobacteraceae} (NR)\\
\nopagebreak
 & Otu00021 & 1859 & \textit{Bacteria}; \textit{Desulfobacterota}; \textit{Desulfobulbia}; \textit{Desulfobulbales}; \textit{Desulfocapsaceae}; \textit{Desulfocapsaceae} (NR)\\
\nopagebreak
 & Otu00025 & 1481 & \textit{Bacteria}; \textit{Desulfobacterota}; \textit{Desulfobulbia}; \textit{Desulfobulbales}; \textit{Desulfocapsaceae}; SEEP-SRB4\\
\nopagebreak
 & Otu00037 & 1209 & \textit{Bacteria}; \textit{Desulfobacterota}; \textit{Desulfobulbia}; \textit{Desulfobulbales}; \textit{Desulfobulbaceae}; \textit{Desulfobulbus}\\
\nopagebreak
 & Otu00033 & 1189 & \textit{Bacteria}; \textit{Desulfobacterota}; \textit{Desulfobulbia}; \textit{Desulfobulbales}; \textit{Desulfocapsaceae}; \textit{Desulfocapsaceae} (NR)\\
\nopagebreak
 & Otu00044 & 1042 & \textit{Bacteria}; \textit{Desulfobacterota}; \textit{Desulfobulbia}; \textit{Desulfobulbales}; \textit{Desulfocapsaceae}; \textit{Desulfocapsaceae} (NR)\\
\nopagebreak
 & Otu00019 & 1012 & \textit{Bacteria}; \textit{Cyanobacteria}; \textit{Cyanobacteriia}; \textit{Cyanobacteriales}; \textit{Xenococcaceae}; \textit{Pleurocapsa}\\
\nopagebreak
\multirow{-10}{8em}{\centering\arraybackslash \textit{Caulerpa cylindracea} (Mixed)} & Otu00046 & 982 & \textit{Bacteria}; \textit{Desulfobacterota}; \textit{Desulfobulbia}; \textit{Desulfobulbales}; \textit{Desulfocapsaceae}; \textit{Desulfotalea}\\
\cmidrule{1-4}\pagebreak[0]
 & Otu00010 & 3572 & \textit{Bacteria}; \textit{Desulfobacterota}; \textit{Desulfobulbia}; \textit{Desulfobulbales}; \textit{Desulfocapsaceae}; \textit{Desulfocapsaceae} (NR)\\
\nopagebreak
 & Otu00011 & 2977 & \textit{Bacteria}; \textit{Desulfobacterota}; \textit{Desulfobacteria}; \textit{Desulfobacterales}; \textit{Desulfosarcinaceae}; \textit{Desulfatitalea}\\
\nopagebreak
 & Otu00013 & 2109 & \textit{Bacteria}; \textit{Proteobacteria}; \textit{Alphaproteobacteria}; \textit{Rhodobacterales}; \textit{Rhodobacteraceae}; \textit{Rhodobacteraceae} (NR)\\
\nopagebreak
 & Otu00021 & 1931 & \textit{Bacteria}; \textit{Desulfobacterota}; \textit{Desulfobulbia}; \textit{Desulfobulbales}; \textit{Desulfocapsaceae}; \textit{Desulfocapsaceae} (NR)\\
\nopagebreak
 & Otu00025 & 1912 & \textit{Bacteria}; \textit{Desulfobacterota}; \textit{Desulfobulbia}; \textit{Desulfobulbales}; \textit{Desulfocapsaceae}; SEEP-SRB4\\
\nopagebreak
 & Otu00033 & 1613 & \textit{Bacteria}; \textit{Desulfobacterota}; \textit{Desulfobulbia}; \textit{Desulfobulbales}; \textit{Desulfocapsaceae}; \textit{Desulfocapsaceae} (NR)\\
\nopagebreak
 & Otu00040 & 1289 & \textit{Bacteria}; \textit{Desulfobacterota}; \textit{Desulfobacteria}; \textit{Desulfobacterales}; \textit{Desulfobacteraceae}; \textit{Desulfobacteraceae} (NR)\\
\nopagebreak
 & Otu00046 & 1089 & \textit{Bacteria}; \textit{Desulfobacterota}; \textit{Desulfobulbia}; \textit{Desulfobulbales}; \textit{Desulfocapsaceae}; \textit{Desulfotalea}\\
\nopagebreak
 & Otu00037 & 1058 & \textit{Bacteria}; \textit{Desulfobacterota}; \textit{Desulfobulbia}; \textit{Desulfobulbales}; \textit{Desulfobulbaceae}; \textit{Desulfobulbus}\\
\nopagebreak
\multirow{-10}{8em}{\centering\arraybackslash \textit{Caulerpa cylindracea} (Monospecific)} & Otu00058 & 950 & \textit{Bacteria}; \textit{Desulfobacterota}; \textit{Desulfobacteria}; \textit{Desulfobacterales}; \textit{Desulfosarcinaceae}; \textit{Desulfatitalea}\\*
\elandscape
